Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-07-09 MUSES_vs_BYOD_solutions.tex
Reviewing @amorag new section 4, and completing with limitations. Closes #24

A MUSES first prototype, implemented on Android devices, has been tested recently. These trials have been conducted in an actual Spanish company (a partner in the European Project where the system is being developed), with 50 employees using the system on their own devices.
The trials were divided in two phases: \textit{silent} and \textit{verbose}, 1 month duration each. During the \textit{silent} phase, MUSES was able to gather data, but without warning the users when a security incident was happening. A total of 23358 security violations were detected. In the \textit{verbose} stage, MUSES started to show warning pop-ups to the users, every time a security incident happened.

As a results, not only the number of security violations were reduced by half in the first two weeks (10977), but the number went on decreasing until it was 0 before the trials period finished. Thus, we can assume that MUSES is an effective tool.

>>>>

A MUSES first prototype, implemented for Android devices, has been recently tested. These trials have been conducted in an actual Spanish company, with 50 employees using the system on their own devices.
% He quitado "(a partner in the European Project where the system is being developed)" porque creo que es irrelevante, y si no se puede redactar de manera que esté fuera de los paréntesis, no debería estar.
The trials were divided in two phases: \textit{silent} and \textit{verbose}, 1 month duration each. During the \textit{silent} phase, MUSES was able to gather data, but without warning the users when a security incident was happening. A total of 23358 security violations were detected. In the \textit{verbose} stage, MUSES started to show warning pop-ups to the users, every time a security incident happened.

As results, not only the number of security violations were reduced by half in the first two weeks (10977), but the number went on decreasing until it was 0 even before the trials period finished. Thus, we can assume that MUSES is an effective tool, even though it has the aforementioned limitation of needing an initial set of defined rules to start working. For this, MUSES also includes a set of guidelines for the companies to build adequate security policies. For instance, the set of initially defined rules used for the trial included a blacklist of forbidden applications, a whitelist of allowed ones, and requirement of antivirus, among others.
